title

### 2013-02-04 paper.tex
MST added
small change

@@

\subsection{Geographical Information}
\begin{figure}
		\centering
        \includegraphics[width=\textwidth]{outlines}
        \caption{Visualization of Shapefile data. For details on the methods used for the Visualization see the "Visualization" section}
        \label{fig:outline}
\end{figure}

@@

Our analyses allow us to make several important conclusions and recommendations
regarding the future of water in the United States. By projecting
future increases in water, we observe that while some parts of the
United States (particularly on the coasts) are not at significant
risk of water shortage by 2025, other parts of the country, particularly
Central America, which already experienced drought in 2012-2013, are
predicted to increase their demands for water in the upcoming years,
and hence will be at risk of \textbf{severe drought}. Moreover, the
area of the country potentially at risk is large, and a significant
portion of the population could be affected. We conclude that there
is significant utility in investing further in water infrastructure
in the United States.

>>>>

\begin{figure}[h]
        \centering
        \includegraphics[width=\textwidth]{graph}
        \caption{Minimal-cost spanning tree of (continental) US counties overlaid on top of US map.}
        \label{fig:graph}
\end{figure}

@@

\subsection{Geographical Information}
\begin{figure}[h]
		\centering
        \includegraphics[width=\textwidth]{outlines}
        \caption{Visualization of Shapefile data. For details on the methods used for the Visualization see the "Visualization" section}
        \label{fig:outline}
\end{figure}

@@

Our analyses allow us to make several important conclusions and recommendations
regarding the future of water in the United States. By projecting
future increases in water, we observe that while some parts of the
United States (particularly on the coasts) are not at significant
risk of water shortage by 2025, other parts of the country, particularly
Central America, which already experienced drought in 2012-2013, are
predicted to increase their demands for water in the upcoming years,
and hence will be at risk of severe drought. Moreover, the
area of the country potentially at risk is large, and a significant
portion of the population could be affected. We conclude that there
is significant utility in investing further in water infrastructure
in the United States.
